\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-25 docs/proposal/doc.tex
Rewrote part on functional connectivity.

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
The functional connectivity describes the statistical dependance of neuronal activity of different brain regions \cite{friston1993functional}.
This gives an insight in the organization of the brain, even though the exact functioning is still unclear.
Functional connectivity is strongly time-dependant, as these dependancies may be short-lasting.
The functional connectivity can be deduced from resting-state networks \cite{Lowe2000, doria2010, Bullmore2009}.

>>>>

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
Functional connectivity describes the statistical dependance of neuronal activity between different brain regions \cite{friston1993functional}.
Functional connectivity can concisely be deduced by measurement of brains in resting-state \cite{Lowe2000, doria2010, Bullmore2009}.
It gives an insight in the organisation of the brain, even though the exact functioning is still unclear.
Functional connectivity is strongly time-dependant, as activity changes rapidly providing only a small time window to measure.
This means measured dependencies can be the result of statistical noise.
